The Power of Two Random Choices

### 2014-03-20 presentation/presentation.tex
change title
add presentation template

\documentclass{beamer}
\let\Tiny=\tiny %to avoid warnings related to font size and beamer 
\usetheme{Amsterdam}
\usecolortheme{dolphin}

\usepackage{stringstrings}

%graphs, pictures
\usepackage{tikz}
\usepackage{pgf}
\usepackage{xxcolor}
\usetikzlibrary{positioning}

\usepackage{comment}

\usepackage[style=numeric-comp,backend=bibtex]{biblatex}
\addbibresource{../sources}

%reduce font size of footnotes
\let\oldfootnotesize\footnotesize
\renewcommand*{\footnotesize}{\oldfootnotesize\tiny}

%---------------------------------------------------------------------
%Front matter
%---------------------------------------------------------------------
\title{The Power of Two Random Choices}
\subtitle{ A follow up seminar to the lecture "Parallel Algorithms"}
\author{Martin Kalany}
\institute
{
  Graduate student in Computer Science\\
  Vienna University of Technology\\
}
\date{\today}

%---------------------------------------------------------------------
%parameters for balls into bins graphs
%---------------------------------------------------------------------
%scale factor
\newcommand\scalefac{0.5}
%diameter of balls
\newcommand\ballsize{5mm}
%number of bins
\newcommand\nrbins{6}
%space between ball and bin
\newcommand\padding{0.1*\ballsize}
%height of a bin
\newcommand\binheight{6*\balldiameter}
%width of a bin
\newcommand\binwidth{\balldiameter}
%gap from bin to bin
\newcommand\bingap{1.6*\balldiameter}
%color of balls

\tikzstyle{ballstyle} = [ball color=black!30!red]

%---------------------------------------------------------------------
%tikz styles and commands
%---------------------------------------------------------------------
\newcommand\balldiameter{2*\ballsize}

%bin style
\tikzstyle{topflat} = [
	minimum width=(\binwidth+2*\padding)*\scalefac, 
	minimum height=(\binheight+5*\padding)*\scalefac,
	append after command={
    		\pgfextra
        		\fill[fill=blue!40] 
        			(\tikzlastnode.north east) [rounded corners] |-
        			(\tikzlastnode.south)  -| 
        			(\tikzlastnode.west) [sharp corners] |- 
        			(\tikzlastnode.north) -- cycle;
	         \draw[rounded corners] 
	         	(\tikzlastnode.north east) |- 
	         	(\tikzlastnode.south) -| 
	         	(\tikzlastnode.north west);
    		\endpgfextra
    }
]

%draw i'th bin
\newcommand\bin[1]{
	\path node[topflat, xshift=#1*\bingap*\scalefac, above, yshift=-\padding*\scalefac]  {};
}

%draw all bins
\newcommand\bins{
	\foreach \ibin in {1,...,\nrbins}
		\bin{\ibin};
}

%paint a ball in bin #1, position #2 
\newcommand\ball[2]{
	\shade[ballstyle] (#1*\bingap,#2*\balldiameter-\ballsize) circle (\ballsize)
}

%put #2 balls into bin 1 <= #1 <= 6
\newcommand\putinbin[2]{
	\ifnum #2 > 0
		\foreach \nrballs in {1,...,#2}
 			\ball{#1}{\nrballs};
 	\fi
}

%put balls into bins. #i: number of balls to put in i'th bin
\newcounter{index}
\newcommand\balls[1]{%
	\getargs{#1}%
  	\setcounter{index}{0}%
  	\whiledo{\theindex < \narg}{%
    		\stepcounter{index}%
    		\putinbin{\theindex}{\csname arg\romannumeral\theindex\endcsname}%
  	}%
}

%draw balls and bins. #i: number of balls to put in i'th bin
\newcommand\bab[1]{%
	\bins
	\balls{#1}
}

%---------------------------------------------------------------------
%document
%---------------------------------------------------------------------
\begin{document}
\frame{\titlepage}

\begin{frame}
\begin{tikzpicture}[scale=\scalefac]

	\bab{1 2 3 4 5 6}

\end{tikzpicture}
\end{frame}

%---------------------------------------------------------------------
%bibliography
%---------------------------------------------------------------------
\begin{frame}[allowframebreaks]
\frametitle<presentation>{Literature}    
\printbibliography
\end{frame} 	 
\end{document}

>>>>

\documentclass[serif,professionalfonts]{beamer}

%\documentclass[a4paper]{article}
%\usepackage{beamerarticle}

%\usepackage{pgfpages}
%\setbeameroption{show only notes}
%\setbeameroption{show notes on second screen=top}

\usetheme{Forcellini}

\usepackage{amsmath}

% \vec makes bold symbols
\def\vec#1{\mathchoice{\mbox{\boldmath$\displaystyle#1$}}
  {\mbox{\boldmath$\textstyle#1$}}
  {\mbox{\boldmath$\scriptstyle#1$}}
  {\mbox{\boldmath$\scriptscriptstyle#1$}}}

% Hermann Zapf Optima clone (wonderful sanserif font) -- URW Classico
\renewcommand{\sfdefault}{uop}
\renewcommand{\rmdefault}{ppl}
\usepackage{eulervm}
\usepackage[right]{eurosym}
% \usepackage{paralist}
\usepackage{algorithm2e}

% professional tables
\usepackage{booktabs}
\usepackage{pdfpages}
\usepackage{multirow}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{subfigure}
\usepackage{epsdice}

\usepackage{fixltx2e}
\usepackage{microtype}

\usepackage{dot2texi}
\usepackage{tikz}
\usetikzlibrary{decorations.pathmorphing,arrows,shapes}

\setbeamertemplate{navigation symbols}{}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{comment}
% description with short indentation
\setbeamersize{description width of=x}

% some math operators
\DeclareMathOperator{\har}{H}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\lag}{lag}
\DeclareMathOperator{\var}{Var}
\DeclareMathOperator{\mf}{\enspace .}
\DeclareMathOperator{\mc}{\enspace ,}
\newcommand{\eye}{\mathbb{I}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\dom}{\{0,1\}^n}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\nats}{\mathbb{N}}
\newcommand{\deq}{\triangleq}
\newcommand{\pd}{\cdot_p}
\newcommand{\pp}{+_p}
\newcommand{\pmn}{-_p}
\newcommand{\ed}{\epsdice}
\newcommand{\bled}{\epsdice[black]}
\newcommand{\bitup}{\vspace*{-4mm}}
\newcommand{\nospace}{\abovedisplayskip=0pt}

\setbeamertemplate{caption}
{
  \raggedright%
  \insertcaption\par%
}

\setbeamercolor{green}{fg=green}

\title{The Power of Two Random Choices}
%\subtitle{ A follow up seminar to the "Parallel Algorithms" lecture}
\author[M. Kalany]{Martin Kalany}
\institute[TU Wien]
{
  Graduate student in Computer Science\\
  Vienna University of Technology\\
}
\date{\today}

\AtBeginSubsubsection[]
{
  \begin{frame}<beamer>
    \frametitle{Outline}
    \tableofcontents[subsubsectionstyle=show/shaded,currentsection,currentsubsection]
  \end{frame}
}

\AtBeginSubsection[]
{
  \begin{frame}<beamer>
    \frametitle{Outline}
    \tableofcontents[subsubsectionstyle=show/shaded,currentsection,currentsubsection]
  \end{frame}
}

\AtBeginSection[]
{
  \begin{frame}<beamer>
    \frametitle{Outline}
    \tableofcontents[subsubsectionstyle=show/shaded,currentsection,currentsubsection]
  \end{frame}
}

\begin{document}
\begin{frame}
  \titlepage
\end{frame}
\note{}

\begin{comment}
\begin{frame}[label=references]
  \frametitle{References}
  %\nocite{*}
  %\setbeamertemplate{bibliography item}[book]
  \bibliographystyle{acm}
  \bibliography{distrib}
\end{frame}
\note{}
\end{comment}

\begin{frame}{Introduction}
\end{frame}
\note{}

%\againframe{references}

\end{document}

\begin{frame}{Title}
\end{frame}
\note{}

%  LocalWords:
